### 2017-03-16 readme.Rmd
update to readme

```{r}
po_v_lampra <- v_lampra[,c("longitude","latitude")]
tassie_preds_two <- stack(tassie_preds,(1 - exp(p_bias_cell*-1)))
names(tassie_preds_two)[8] <- 'bias'

@@

```{r,fig.height=8,fig.width=12}
fm_v_lampra_w_s <- gam(presence/weights ~ s(annual_mean_temperature) +
                                      s(annual_precipitation) +
                                      s(max_temperature_of_warmest_month) +
                                      s(min_temperature_of_coldest_month) +
                                      s(precipitation_of_driest_month) +
                                      offset(log(bias)),
                                      weights = weights,
                                      data = bkpts_v_lampra,
                                      family = poisson())

>>>>

```{r}
po_v_lampra <- v_lampra[,c("longitude","latitude")]
tassie_preds_two <- stack(tassie_preds,(1-exp(p_bias_cell*-1)))
names(tassie_preds_two)[8] <- 'bias'

@@

```{r,fig.height=8,fig.width=12}
fm_v_lampra_w_s <- gam(presence/weights ~ s(annual_mean_temperature) +
                                      s(annual_precipitation) +
                                      s(max_temperature_of_warmest_month) +
                                      s(min_temperature_of_coldest_month) +
                                      s(precipitation_of_driest_month),
                                      offset=log(bias),
                                      weights = weights,
                                      data = bkpts_v_lampra,
                                      family = poisson())
